Place of death in NRS COVID-19 deaths

### 2021-08-24 covid_nrs_place_of_death_visualisations.Rmd
made a plot of proportions of covid by whether underlying or contributory

```{r}
(figure_covid_contributory_vs_underlying_cause <-
annual_covid_contributory_vs_underlying_cause %>%
  pivot_longer(cols = -c(year, place_of_death, deaths_covid_related), names_to = "covid_category", values_to = "value") %>%
  extract(col = covid_category, into = c("measure", "covid_category"), regex = "(covid_19|proportion)_(.*)", remove = TRUE) %>%
  mutate(
    measure = if_else(measure == "covid_19", "n", measure),
    covid_category = str_remove(covid_category, pattern = "\\_.*$"),
    covid_category = paste0(covid_category, " cause")
  ) %>%
  ggplot(aes(x = place_of_death, y = value, group = covid_category, fill = covid_category)) +
    facet_wrap(year~measure,scales = "free", nrow = 3) +
    geom_col(position = position_dodge(width = 1))
)
```

>>>>

```{r}
(figure_covid_contributory_vs_underlying_cause <-
annual_covid_contributory_vs_underlying_cause %>%
  pivot_longer(cols = -c(year, place_of_death, deaths_covid_related), names_to = "covid_category", values_to = "value") %>%
  extract(col = covid_category, into = c("measure", "covid_category"), regex = "(covid_19|proportion)_(.*)", remove = TRUE) %>%
  mutate(
    measure = if_else(measure == "covid_19", "n", measure),
    covid_category = str_remove(covid_category, pattern = "\\_.*$"),
    covid_category = paste0(covid_category, " cause"),
    year = str_replace(year, pattern = "2021", replacement = "2021*"),
    year = factor(year, levels = c("2020", "2021*", "2020-2021*")),
    place_of_death = factor(place_of_death, levels = c("Hospital", "Home & other non-institution", "Care home"))
  ) %>%
  filter(measure =="proportion") %>%
  filter(place_of_death != "Other") %>%
  ggplot(aes(x = place_of_death, y = value, group = covid_category, fill = covid_category)) +
    facet_grid(~year) +
    geom_col(position = position_stack()) +
    # geom_col(position = position_dodge(width = 1)) +
    scale_y_continuous(labels = function(x) scales::percent(x, accuracy = 1)) +
    scale_fill_viridis_d(labels = c("Contributory", "Underlying")) +
    # geom_text(data = . %>% filter(covid_category == "contributory cause"), inherit.aes = TRUE, aes(label = paste0("Contributory cause: ", scales::percent(value, accuracy = 0.1))), x = 0.7, nudge_y = -0.2, hjust = 1) +
    # geom_text(data = . %>% filter(covid_category == "underlying cause"), inherit.aes = TRUE, aes(label = paste0("Underlying cause: ", scales::percent(value, accuracy = 0.1))), x = 0.5, nudge_y = 0.2, hjust = 1) +
    geom_label(data = . %>% filter(covid_category == "contributory cause"), inherit.aes = TRUE, aes(label = scales::percent(value, accuracy = 0.1), y = 1.02-value), fill = "white",  hjust = 0.5) +
    geom_label(data = . %>% filter(covid_category == "underlying cause"), inherit.aes = TRUE, aes(label = scales::percent(value, accuracy = 0.1), y = value-0.2), fill = "white", hjust = 0.5) +
    labs(
      x = NULL, y = NULL,
      subtitle = paste0(c(paste0("* ",only_2021_text)),collapse="\n"),
      caption = paste0(c(source_nrs_text),collapse="\n")
      ) +
    guides(fill = guide_legend(nrow=1, title = NULL)) +
    theme(
      legend.position = "top",
      legend.text = element_text(size = 10),
      plot.caption = element_text(size = 10, colour = "gray60"),
      axis.text.x = element_text(angle = 45, hjust = 1, size = 8)
      ) +
    NULL
)

save_output_file(filename = paste0(dir_outputs,"/figure_covid_contributory_vs_underlying_cause"), extensions = c(".pdf",".svg",".png"), plot = figure_covid_contributory_vs_underlying_cause, width = 6, height = 6, units = "in", dpi = 300)
```
